### 2015-04-25 evaluation.tex
fixed caption in table 1
updates to the evaluation

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rrr rrr rr r r}
\centering
\input{experiments/tables/granularity.tex}
\end{tabular}
\caption{Data race analysis and scalability results.}
\label{tab:races}
\end{table*}

@@

We conducted all experiments on ... We use the following software versions: Clang/LLVM 3.5; SMACK 1.4; Z3 4.1; \corral commit 3aa62d7425b5; Boogie commit d6a7f2bd79c9.

All reported times are in seconds and averages of N executions. We report: lines of C code (LoC); number of entry point pairs (\#Pairs); memory regions in the program (\#MRs); the number of racy memory regions that \whoop found (\#Racy MRs); the number of race reports that \whoop generated (\#Race Reports); the number of races that \corral found (same in all configurations).

@@

@@

We evaluate the scalability of our acceleration technique with respect to our benchmark sets.

Our experiments use the default \corral context switch bound \texttt{/k:2}. A higher context switch bound would result into deeper interleavings being explored and thus a larger sequentialized program. Intuitively, this means that we would see even greater speedups using information from \whoop, when exploring deeper interleavings. \PDComment{We should take a few measurements with higher k -- no need to be in the table -- just to verify this argument.}

@@

In Table~\ref{tab:races}, we can notice that \whoop is much faster than \corral. For example, \whoop analyses the dtlk char driver in 6.51 seconds, whereas \corral requires 1287.05 seconds.

>>>>

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\caption{Program statistics and data race detection results from running \whoop and \corral on our benchmarks. Corral uses a context switch bound of 2.}
\label{tab:stats}
\begin{tabular}{l rrr rr r}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\end{table}

\begin{table*}[t]
\small
\centering
\caption{Runtime comparison with different yield instrumentation granularities and context-switch bounds (csb).}
\label{tab:results}
\begin{tabular}{l rrr rrr rr r r}
\centering
\input{experiments/tables/scalability.tex}
\end{tabular}
\end{table*}

%\begin{table*}[t]
%\small
%\centering
%\caption{Program statistics, analysis and scalability results. Corral uses a context switch bound of 2.}
%\label{tab:races}
%\begin{tabular}{l rrr rrr rr r r}
%\centering
%\input{experiments/tables/granularity.tex}
%\end{tabular}
%\end{table*}
%
%\begin{table*}[t]
%\small
%\centering
%\caption{Analysis and scalability results. Corral uses a context switch bound of 5 and 9, respectively.}
%\label{tab:races2}
%\begin{tabular}{l rr r r rr r r}
%\centering
%\input{experiments/tables/granularity2.tex}
%\end{tabular}
%\end{table*}

@@

All experiments were performed on a ... machine running ..., LLVM 3.5; SMACK 1.5; Z3 4.3.2; Boogie rev. 4192 and \corral rev. 534.

@@

Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs that \whoop identified (\#Racy Pairs); number of racy memory regions that \whoop reported (\#Racy MRs); and number of races that \corral discovered (\#Races Found).

@@

We evaluate the scalability of our acceleration technique with respect to our benchmark sets (Table~\ref{tab:results}). All reported times are in seconds and averages of three runs. \corral was configured with a time budget of 3000 seconds per tool invocation (one for each pair of entry points); \whoop did not use a timeout.

Our experiments use the \corral context switch bounds \texttt{/k:2}, \texttt{/k:5} and \texttt{/k:9}. A higher context switch bound would result into deeper interleavings being explored and thus a larger sequentialized program. Intuitively, this means that we would see even greater speedups using information from \whoop, when exploring deeper interleavings.

@@

In Table~\ref{tab:results}, we can notice that \whoop is much faster than \corral. For example, \whoop analyses the dtlk char driver in 6.51 seconds, whereas \corral requires 1287.05 seconds.

% We did not discover any data races with larger context switch bounds.
